Boutiques: a flexible framework for automated application integration in computing platforms

### 2017-10-13 paper.tex
Put @gkiar 2nd author

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
        Krzysztof J. Gorgolewski, Charles G. Guttmann, Gregory Kiar, Nathaniel Kofalt, \\
        Pierre-Olivier Quirion, Pierre Rioux, Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}

>>>>

\author{Tristan Glatard, Gregory Kiar, Tristan Aumentado-Armstrong,
  Natacha Beck, Pierre Bellec,\\ Remi Bernard, Sorina Camarasu-Pop,
  Fr\'ed\'eric Cervenansky, Samir Das, \\ Rafael Ferreira da Silva,
  Guillaume Flandin, John Flavin, Pascal Girard, \\ Krzysztof
  J. Gorgolewski, Charles G. Guttmann, Val\'erie Hayot-Sasson,
  Nathaniel Kofalt, \\ Pierre-Olivier Quirion, Pierre Rioux,
  Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}
